### 2025-06-20 modern-portfolio-theory.qmd
20250620 - fix duplicate labels

@@

>>>>

```{r}
#| label: fig-projectedPointsMeanVsSDPDF
#| fig-cap: "Mean of Projected Fantasy Points For Each Player as a Function of the Standard Deviation of the Projected Fantasy Points Across Sources."
#| fig-alt: "Mean of Projected Fantasy Points For Each Player as a Function of the Standard Deviation of the Projected Fantasy Points Across Sources."

@@

```{r}
#| label: fig-fantasyPointsMeanVsSDPDF
#| fig-cap: "Mean of Weekly Fantasy Points For Each Player as a Function of the Week-to-Week Standard Deviation of their Fantasy Points."
#| fig-alt: "Mean of Weekly Fantasy Points For Each Player as a Function of the Week-to-Week Standard Deviation of their Fantasy Points."
